Astrophysical calibration of gravitational-wave detectors

### 2015-11-06 docs/cosmic_cal.tex
Added in prep reference for CW work

% comparative calibration
A further application of astrophysical calibration is the relative calibration
of \ac{GW} detectors.  In this case we would be interested in obtaining
posterior distributions on the ratios of calibration scale factors between
detectors. For \ac{CBC} events, in this scenario there would be no explicit
requirement for a redshift measurement and therefore a cosmologically inferred
distance. There would however be a requirement for an electromagnetically
inferred sky position of $O(\rm{degrees})$ accuracy. A more suitable source for
relative calibration estimation would be that of continuous \ac{GW} emission.
In that case, sky position and orientation information would be obtained to a
high level of accuracy from single detector analyses alone. A primary use for
relative calibration information would be to account for potential biases in
the sky position estimates for \ac{CBC} and burst sources. In this case,
amplitude information is a secondary, but important factor, in breaking
degeneracies on sky position estimates.

>>>>

% comparative calibration
A further application of astrophysical calibration is the relative calibration
of \ac{GW} detectors.  In this case we would be interested in obtaining
posterior distributions on the ratios of calibration scale factors between
detectors. For \ac{CBC} events, in this scenario there would be no explicit
requirement for a redshift measurement and therefore a cosmologically inferred
distance. There would however be a requirement for an electromagnetically
inferred sky position of $O(\rm{degrees})$ accuracy. A more suitable source for
relative calibration estimation would be that of continuous \ac{GW} emission.
In that case, sky position and orientation information would be obtained to a
high level of accuracy from single detector analyses alone. A primary use for
relative calibration information would be to account for potential biases in
the sky position estimates for \ac{CBC} and burst sources (Vitale, Messenger \& Pitkin, in preparation). In this case,
amplitude information is a secondary, but important factor, in breaking
degeneracies on sky position estimates.
